An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-10-26 neurips-19/poly-embed.tex
Responding to Raf's questions

\raf{I am not sure this is the place to clarify these connections.  I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.  If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.  E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.  Jessie, feel free to give it a shot.}
\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\bo{Removed comments to point to appendix, since that creates more links...}
Appendix~\ref{app:calibration} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
\begin{equation}
\ell^{top-k}(r,y) = \begin{cases}
0 & r_y = \bar r_{-y} + 1\\
\bar r - \frac 1 k & r_y = 1\\
1 + \bar r & r_y = 0
\end{cases}~,~
\end{equation}
where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

@@

\hrule
\bigskip
TODO for camera-ready (tagging the person who'll probably end up doing it)
\begin{enumerate}
	\item \jessie{Make poster and link to it online}
	\item All: Address todos in paper.
	\item OPTIONAL: Make/link to slides and/or on paper
	\item Reviewer 1 (Didn't change review)
	\begin{enumerate}
		\item Clarify terms like \emph{reports} and \emph{properties}. \jessie{Done}
	\end{enumerate}
	\item Reviewer 2 (didn't change review)
	\begin{enumerate}
		\item Motivate polyhedral losses
		\item Definitions 1-3 intuition \jessie{Done}
	\end{enumerate}
	\item Reviewer 3 (didn't change review)
	\begin{enumerate}
		\item Add discussion on the computational complexity (or lack thereof) of constructing $L$ and $\psi$.
		\item \jessie{Make sure we have corrected top-$k$ proof.}
	\end{enumerate}
	\item Meta-Review: ``Inserting all the comments made to answers R2 and R3 is a must for the paper to be very good.''
\end{enumerate}

>>>>

\raf{I am not sure this is the place to clarify these connections.  I added a forward reference to \S~\ref{sec:links-embeddings} at the top of this section, saying we'll move to the $\X\times\Y$ setting then, and I wonder if that's all we need to do.  If we want to do more, I think \S~\ref{sec:links-embeddings} would be the place to do it.  E.g.\ we can discuss $\Gamma(\Pr[Y\mid X=x])$ and $\gamma$, etc., using the notation at the end of \S~\ref{sec:property-elicitation}.  Jessie, feel free to give it a shot.}
\jessie{I think the forward reference is enough.  We told a reviewer we would clarify what reports are, but that also might be as simple as clarifying report = prediction.}
\proposedadd{When we discuss \emph{reports}, we are talking about the prediction yielded by $h(x)$ for the learned hypothesis function $h : \X \to \R$ over the input space $\X$.  In this case, we can think of $p$ as the conditional probability $p = Pr[Y = y | X = x]$ when the true distribution is over $\X \times\Y$.  Throughout, we abstract away the input $X \sim \X$ and can work with these conditional probabilities $p \in \simplex$.}
Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, \proposedadd{; that is, $\Gamma(p)$ is the prediction that minimizes expected loss when the outcome $Y \sim p$.  Moreover, \ldots} and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\btw{Finite property note commented out}%(Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.)
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

\bo{Removed comments to point to appendix, since that creates more links...}
Appendix~\ref{app:calibration} in the full version~\cite{finocchiaro2019embedding} contains the full proof; this section provides a sketch along with the main construction and result.
The first step is to give a link $\psi$ such that exactly minimizing expected surrogate loss $L$, followed by applying $\psi$, always exactly minimizes expected original loss $\ell$.
The existence of such a link is somewhat subtle, because in general some point $u$ that is far from any embedding point can minimize expected loss for two very different distributions $p,p'$, making it unclear whether there exists a link choice $\psi(u)$ that is simultaneously optimal for both.
We show that as we vary $p$ over $\simplex$, there are only finitely many sets of the form $U = \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ (Lemma~\ref{lem:polyhedral-range-gamma}).
Associating each $U$ with $R_U \subseteq \R$, the set of reports whose embedding points are in $U$, we enforce that all points in $U$ link to some report in $R_U$.
(As a special case, embedding points must link to their corresponding reports.)
Proving this is well-defined uses a chain of arguments involving the Bayes risk, ultimately showing that if $u$ lies in multiple $U$, the corresponding report sets $R_U$ all intersect at some $r =: \psi(u)$.

@@

\jessie{Don't think we need the below addition for the camera ready, but will eventually want something along these lines for the arXiv version.}
\proposedadd{To generalize this result, first consider that Lapin's surrogate is polyhedral, and we propose that each coordinate of an optimal report $u \in \reals_+^n$ must be at one of three points: $0$, $1$, or another ``high'' point that is a function of the number of high points and $M = |\{i : u_i = 1\}|$.  Since there are only a finite number of such optimal reports, $\R$, we know that this embeds a finite loss, namely $L^2_\R$.
\begin{align*}
\R := \left\{ \frac{|M| + k -1}{k - |H|} \mathbf{1}_H + \mathbf{1}_M : H, M \subset [n], H\cap M = \emptyset, |H| + |M| \leq k \right\}
\end{align*}
The discrete loss $\ell^{top-2} = L^2|_\R$ is then defined as follows:
\begin{equation}
\ell^{top-k}(r,y) = \begin{cases}
0 & r_y = \bar r_{-y} + 1\\
\bar r - \frac 1 k & r_y = 1\\
1 + \bar r & r_y = 0
\end{cases}~,~
\end{equation}
where $\bar r = \frac 1 k \sum_{i=1}^k r_{[i]}$.
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion and Future Directions} \label{sec:conclusion}
% \paragraph{Summary.}
This paper formalizes an intuitive way to design convex surrogate losses for classification-like problems---by embedding the reports into $\reals^d$.
We establish a close relationship between embedding and polyhedral surrogates, showing both that every polyhedral loss embeds a discrete loss (Theorem~\ref{thm:poly-embeds-discrete}) and that every discrete loss is embedded by some polyhedral loss (Theorem~\ref{thm:discrete-loss-poly-embeddable}).
We then construct a calibrated link function from any polyhedral loss to the discrete loss it embeds, giving consistency for all such losses.
We conclude with examples of how the embedding framework presented can be applied to understand existing surrogates in the literature, including those for the abstain loss, top-$k$ loss, and Lov\'asz hinge.\bo{commented stuff for space}
\raf{Is this in response to some reviewer, or just because we had to comment stuff for space?}
\jessie{What we had commented for space}
\proposedadd{We use our link construction to understand calibrated links for abstain different than the one given by~\citet{ramaswamy2018consistent}.
While one top-$k$ surrogate has already been shown to be inconsistent, we show the similar discrete loss that the surrogate embeds.
Finally, we use our framework to prove the inconsistency of the Lov\'asz Hinge.}

@@
